---
title: "got_dti?"
author: "moriahstendel"
date: "7/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rio)
library(tidyverse)
library(plyr)
library(dplyr)
library(data.table)
library(reshape)

knitr::opts_knit$set(root.dir = "~/Documents/rockland_behavior")
```

Does DTI data exist for the measures we are interested in?

### Import Data
```{r}
data <- import("wrangled_behav_data.csv")
```

### Measures of interest

* demographics
* age (16+)
* asq
* temperament
* bdi
* stress resiliency
* risk taking
* dot probe
* emotional regulation
* interpersonal reactivity
* attention network task
* big five
* drug use
* worry
* perservative thinking
* rumination
* social networking
* stai
* trauma - adult
* trauma - child
* affect
* self report - adult
* self report - youth

### Get correct age range

```{r}

# add new age column to combine age from multiple csvs
# if the calculated age column is empty, pull from the demographics questionnaire (from same visit)

for (row in 1:nrow(data)){
  if (is.na(data[row,'AGE_04'])){
    data[row,'AGE_04'] <- data[row, 'DEM_001']
  }
}

# select individuals between 16 and 69
data <- subset(data, DEM_001>16 & DEM_001 < 69)

```

### Remove rows without DTI data

```{r}
data <- subset(data, has_dti ==1)

```

### count data points for measures of interest

```{r}
length(which(!is.na(data$ASSQ_05))) # 17, autism spectrum quotient
length(which(!is.na(data$ATQ_02))) # 88, temperament
length(which(!is.na(data$BIR_3))) #235, resiliency to distress
length(which(!is.na(data$DOSP_02))) #69, social risk taking
length(which(!is.na(data$DOT_02))) #6, dot probe task
length(which(!is.na(data$IPRI_02))) #81, interpersonal reactivity index 
length(which(!is.na(data$ANT_02))) #469, attention network task
length(which(!is.na(data$NEOFFI_02))) #451, big five
length(which(!is.na(data$NIDA_02))) #83, drug use
length(which(!is.na(data$CCDPSWQ_02))) #1, penn worry questionnaire
length(which(!is.na(data$CCDERQ_02))) #1, emotional reactivity index
length(which(!is.na(data$PTQ_002))) #1, perservative thinking questionnnaire
length(which(!is.na(data$RRS_002))) #1, ruminative response scale
length(which(!is.na(data$SOCIAL_02))) #467, social network questionnaire
length(which(!is.na(data$DSEQ_02))) #451, State Trait Anxiety
length(which(!is.na(data$TSC40_02))) #447, trauma questionnaire scale, adult
length(which(!is.na(data$TSCC_02))) #14, trauma questionnaire child 
length(which(!is.na(data$CCDAIM_02))) #1, affect intensity measure 
length(which(!is.na(data$ASRM_02))) #84, youth self-report
length(which(!is.na(data$YSR_02))) #12, #98 total for self-report
length(which(!is.na(data$DBDI_02))) #84

```

