---
title: "wranglerock"
author: "mstendel"
date: "6/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set working directory
knitr::opts_knit$set(root.dir = "/Users/chavezlabadmin/Documents/rockland_behavior")

#install packages
library(rio)
library(tidyverse)
library(plyr)
library(dplyr)
library(data.table)
library(reshape)
```

This code will extract the relevant data from rockland csv files for measures of interest to create a final document containing itemized measures (when extant), total scores, and for whom what data exists.

## create function to turn first row of data into colnames

We will need to use this later. 

```{r column name creation}
header.true <- function(df){
  names(df) <-as.character(unlist(df[1,]))
  df[-1,]
}

```

## affixation script

### import data sets of interest

load in data:
``` {r }

# these are the datasets i am interested in but can be changed to whatever suits your fancy
# this import process is clunky, if someone can make it better please help

df_1 <- import("Demos/8100_Demos_20190312.csv") #demographics
df_2 <- import("Age/8100_Age_20190312.csv") #age
df_3 <- import("ASSQ/8100_ASSQ_20190312.csv") #high-functioning autism spectrum questionnaire
df_4 <- import("ATQ/8100_ATQ_20190312.csv")  #adult temperament measure
df_5 <- import("ATQ/8100_ATQ_20190312.csv") #beck depression inventory 2
df_6 <- import("Bird/8100_Bird_20190312.csv") #behavioural index of resiliency to stress
df_7 <- import("Diagnostic_Summary/8100_Diagnostic_Summary_20190312.csv") # do they meet criteria for DSM-IV diagnosis? 
df_8 <- import("DOSPERT/8100_DOSPERT_20190314.csv") #domain specific risk taking (specifically interested in social domain)
df_9 <- import("Dot_Probe/8100_Dot_Probe_20190314.csv") #dot probe (measure of selective attention to threatening stim)
df_10 <- import("EHQ/8100_EHQ_20190314.csv") #handedness - maybe important for brain data?? 
df_11 <- import("ERQ/8100_ERQ_20190314.csv") #emotional regulation index
df_12 <- import("IRI/8100_IRI_20190314.csv") # interpersonal reactivity index 
df_13 <- import("ANT/8100_ANT_20190312.csv") #attention network task
df_14 <- import("MRI_LS/8100_MRI_Log_Sheet_20190314.csv") #log of mri information
df_15 <- import("NEO-FFI-3/8100_NEO-FFI-3_20190314.csv") #big five inventory
df_16 <- import("NIDA/8100_NIDA_(3-19-13)_20190314.csv") #brief self report on drug use  
df_17 <- import("PSWQ/8100_PSWQ_20190314.csv") # penn state worry questionnaire
df_18 <- import("PTQ/8100_PTQ_20190314.csv") #perservative thinking questionnaire
df_19 <- import("RRS/8100_RRS_20190314.csv") #ruminative response scale 
df_20 <- import("Social_Network/8100_Social_Network_20190314.csv") #social networking questionnaire
df_21 <- import("STAI/8100_STAI_20190314.csv") #state trait anxiety
df_22 <- import("TSC-40/8100_TSC-40_20190314.csv") #trauma symptoms - adult
df_23 <- import("TSC-C/8100_TSC-C_20190314.csv") #trauma symptoms - child
df_24 <- import("AIM/8100_AIM_20190308.csv") #affect intensity measure
df_25 <- import("ASR/8100_ASR_20190312.csv") #self report (clinical measures) - ADULT
df_26 <- import("YSR/8100_YSR_20190314.csv") #self report (clinical measures) - YOUTH

#how many data sets you have, here 26
num_of_data_sets <- 26

#create a list of all the data files you imported
df_list <- lapply(paste('df_', seq(1, num_of_data_sets), sep=''), get)

#remove the columns we don't care about ("Subject Type", "Sub Study Label", "Days since first enrollment", "Days since sub study enrollment"))
df_list <- lapply(df_list, function(x) x[-c(2,3,4,6)])


```

## create variable key

``` {r}
# define function "make.key" to create key for any data file 
key_temp <- NA
key_file <- NA
make.key <- function(df){
  key <- matrix((df[1,]), ncol=1)
  colnames(key) = "key"
  item <- as.vector(colnames(df))
  key_temp <<- cbind(key, item)
  key_file <<- rbind(key_temp, key_file) 
}

# get key for each individual data file and store in one list, key_file
lapply(df_list, make.key)

#remove duplicate rows in key file
key_file <- key_file %>% 
  unique()
key_file <- as.data.frame(key_file)
rownames(key_file) <- seq(1, nrow(key_file))

#save to csv  
fwrite(key_file, file ="rockland_key.csv")
```

## create basefile

this will get a list of every participant at every visit to create a base file which we can affix other data to. 

```{r}

#set up empty variables
subjects <- NA
temp_col <- NA

#create function to get the columns of each data frame and bind to a list of subjects
get.columns <- function(df){
  id <- matrix((df[,1]), ncol = 1)
  visit <- matrix((df[, "Visit"]))
  temp_col <<- cbind(id,visit)
  subjects <<- rbind(temp_col,subjects) %>% 
    unique()
}

#apply above function to all dataframes of interest - this will be a base file of all subjects and visits
lapply(df_list, get.columns) 
dataset <- as.data.frame(subjects)
dataset <- header.true(dataset)
rownames(dataset) <- seq(1, nrow(dataset))
  
```


### affix data from each dataset to correct participant and visit

```{r}

# use first row of data in all sets as the column names
df_list <- lapply(df_list, header.true)

#merge data by id & visit

final_data <- merge_recurse(df_list, by = c('ID', 'VISIT'))
```
### combine age data across multiple vars

```{r}
for (row in 1:nrow(final_data)){
  if (is.na(final_data[row,'AGE_04'])){
    final_data[row,'AGE_04'] <- final_data[row, 'DEM_001']
  }
}

```

### check if dti data exists for this participant
```{r}

dti <- as.data.frame(list.files(path = "/Users/chavezlabadmin/Documents/rockland_data/FA_ANTs_collection"))
colnames(dti) <- "dti_filename"
ID <- substr(dti$dti_filename, 1, 9)

dti <- cbind(dti, ID)  

#add dti file name -- 
# need to find out what session they did DTI on, though!! not sorted by visit #. where is this info?
final_data <- left_join(final_data, dti, by = "ID")

#add a DTI yes/no column
final_data$has_dti <- NA

for (row in 1:nrow(final_data)){
  if (is.na(final_data[row, "dti_filename"])){
    final_data[row, "has_dti"] <- 0
  }
    else {
    final_data[row, "has_dti"] <- 1
    }
  }

``` 

### write the data to a CSV
```{r}
fwrite(final_data, file= "wrangled_behav_data.csv")
``` 
